---
title: "Assessment of Impact of COVID19"
author: "Frank NAMUGERA"
date: '`r as.Date(Sys.time())`'
output: html_document
---

```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
library(plyr)
library(dplyr)
library(ggplot2)
library(stringr)
library(janitor)
library(knitr)
library(reshape2)
library(tidyr)
library(data.table)
library(readxl)
```

```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata<- readxl::read_xlsx("D:/Learnings/work/OJ/COVID19 Impact study/Study_on_the_Impact_of_COVID-19_on_the_Tourism_Industry_in_Uganda_in_the_last_one_year_March_2020-March_2021_-_all_versions_-_labels_-_2021-04-09-15-19-13.xlsx", sheet = 'Study on the Impact of COVID...')
#covdata<-readRDS("C:/Users/Derrick pc/Desktop/covid/R-codes-Derrick/covdata.RDS")
```

### Details of the Tourism Establishments
Table 1: Respondents by Type of Business

```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% group_by(`2. Type of Business`) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row')  %>% kable()

```

Table 2: Demographics of the Respondents
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(Respondent = case_when(
  str_detect(`Other (Specify)...7`, 'Receptionist|Reception') ~ 'Receptionist', 
  str_detect(`Other (Specify)...7`, 'owner|Owner')~'CEO' , 
   str_detect(`Other (Specify)...7`, 'Managing director|manager|General Manager|Director|Manager')~'Director/Manager',
    str_detect(`Other (Specify)...7`, 'Accountant|accountant')~'Accountant' , 
  TRUE ~ `2. What is the Position of the Respondent?` )) %>% group_by(Respondent) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where =  'row') %>% kable()


```

Table 3: Years in Business										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% group_by(`4. Years in Business of the Company`) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row') %>% kable()

```

Table 4: Years in Business and Business Type										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% group_by(`4. Years in Business of the Company`, `2. Type of Business`) %>% summarise(Count = n()) %>% pivot_wider(names_from = `2. Type of Business`, values_from = 'Count') %>% adorn_totals(where = c('row', 'col')) %>% kable()  #%>% mutate(Per = paste0(round(Count/sum(Count)*100), '%'))

```

Table 5: Employees by Establishment										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`5. Approximately how many employees are there in your organization?` = factor(`5. Approximately how many employees are there in your organization?`, levels = c('0-10 employees', '11-20 employees', '21-30 employees', '31-40 employees', '41-50 employees', 'Over 50 employees', 'Over 100 employees'))) %>% group_by(`5. Approximately how many employees are there in your organization?`) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row') %>% kable()

```

Table 6: Employees by Years in Business of a company
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`5. Approximately how many employees are there in your organization?` = factor(`5. Approximately how many employees are there in your organization?`, levels = c('0-10 employees', '11-20 employees', '21-30 employees', '31-40 employees', '41-50 employees', 'Over 50 employees', 'Over 100 employees')), `4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% group_by(Numer_of_Employees = `5. Approximately how many employees are there in your organization?`, `4. Years in Business of the Company`) %>% summarise(Count = n()) %>% pivot_wider(names_from = `4. Years in Business of the Company`, values_from = 'Count') %>% adorn_totals(where = c('row', 'col')) %>% kable()

```

Table 7: Employees by Business Type								

```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`5. Approximately how many employees are there in your organization?` = factor(`5. Approximately how many employees are there in your organization?`, levels = c('0-10 employees', '11-20 employees', '21-30 employees', '31-40 employees', '41-50 employees', 'Over 50 employees', 'Over 100 employees')), `4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% group_by(Numer_of_Employees = `5. Approximately how many employees are there in your organization?`, `2. Type of Business`) %>% summarise(Count = n()) %>% pivot_wider(names_from = `2. Type of Business`, values_from = 'Count') %>% adorn_totals(where = c('row', 'col')) %>% kable()
```


Table 8: Services offered by Tourism Businesses
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% group_by(`4. Years in Business of the Company`) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row') %>% kable()

```

Business Performance									
Table 9: Business Performance										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`7. How do you rate your business performance in the last 12 months?` = factor(`7. How do you rate your business performance in the last 12 months?`, levels = c('Poor', 'Fair', 'Good'))) %>% group_by(`7. How do you rate your business performance in the last 12 months?`) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row') %>% kable()
```

Table 10: Business Performance	
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`7. How do you rate your business performance in the last 12 months?` = factor(`7. How do you rate your business performance in the last 12 months?`, levels = c('Poor', 'Fair', 'Good'))) %>% group_by(`7. How do you rate your business performance in the last 12 months?`, `2. Type of Business`) %>% summarise(Count = n()) %>% pivot_wider(names_from = `7. How do you rate your business performance in the last 12 months?`, values_from = `Count`)   %>% kable()
```

Table 11: Years in Business and Business Performance										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% mutate(`7. How do you rate your business performance in the last 12 months?` = factor(`7. How do you rate your business performance in the last 12 months?`, levels = c('Poor', 'Fair', 'Good')), `4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% group_by(`7. How do you rate your business performance in the last 12 months?`, `4. Years in Business of the Company`) %>% summarise(Count = n()) %>% pivot_wider(names_from = `7. How do you rate your business performance in the last 12 months?`, values_from = `Count`)   %>% kable()
```

Employment										
Table 12: Workdforce status 										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`17a. What was your total number of workers before COVID-19?`:`17e. How many of your workers are facing pay cut due to the pandemic?`) %>% reshape2::melt() %>% group_by(variable) %>% summarise(value = sum(value, na.rm = T))  %>% kable()
```

Table 13: Status of Workforce by Tourism Industry							
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`2. Type of Business`,  `17a. What was your total number of workers before COVID-19?`:`17e. How many of your workers are facing pay cut due to the pandemic?`) %>% reshape2::melt(id = "2. Type of Business") %>% group_by(`2. Type of Business`,variable) %>% summarise(value = sum(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from = 'value') %>% adorn_totals(where = c('row', 'col')) %>% kable()
```

Table 14: Workdforce status by Hotel										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`1. What is the Company/Organisation/Business name?`,  `17a. What was your total number of workers before COVID-19?`:`17e. How many of your workers are facing pay cut due to the pandemic?`) %>% reshape2::melt(id = "1. What is the Company/Organisation/Business name?") %>% group_by(`1. What is the Company/Organisation/Business name?`,variable) %>% summarise(value = sum(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from = 'value') %>% adorn_totals(where = c('row', 'col')) %>% kable()
```

Table 15: Status of current Workforce										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% group_by(`18. Have you downsized/ increased your work force in the last 12 months?`) %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row') %>% left_join(
covdata %>% select(Increased = `19a. By what percentage have you increased your workforce?`, Downsized = `19b. By what percentage have you downsized your workforce?`) %>% reshape2::melt() %>% group_by(`18. Have you downsized/ increased your work force in the last 12 months?` = variable) %>% summarise(Mean =paste0(round(mean(value, na.rm = T)), "%"))) %>% kable()
```

Table 16: Status of current Workforce by Tourism Industry:
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% group_by(`18. Have you downsized/ increased your work force in the last 12 months?`, `2. Type of Business`) %>% summarise(Count = n()) %>% pivot_wider(names_from = `18. Have you downsized/ increased your work force in the last 12 months?`, values_from = `Count`)  %>% adorn_totals(where =c('row', 'col'))  %>% kable()
```

Occupancy Levels and Room Cancellations in 2021										
Table 17: Mean Percentage Occupancy levels										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`20a. What was your Occupancy level for Jan 2021`:`20c. What was your Occupancy level for Mar 2021`) %>% reshape2::melt() %>% mutate(Month = case_when(str_detect(variable, 'Jan')~ 'Jan', str_detect(variable, 'Feb')~ 'Feb', str_detect(variable, 'Mar')~ 'Mar', )) %>% mutate(Month = factor(Month, levels = month.abb)) %>% group_by(Month) %>% summarise(Mean_occupancy =round(mean(value, na.rm = T))) %>% rbind(covdata %>% select(`20a. What was your Occupancy level for Jan 2021`:`20c. What was your Occupancy level for Mar 2021`) %>% reshape2::melt() %>% mutate(Month = case_when(str_detect(variable, 'Jan')~ 'Jan', str_detect(variable, 'Feb')~ 'Feb', str_detect(variable, 'Mar')~ 'Mar', )) %>% mutate(Month = 'Average') %>% group_by(Month) %>% summarise(Mean_occupancy =round(mean(value, na.rm = T))))  %>% kable()
```

Table 18: Occupancy levels by Hotel										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`20a. What was your Occupancy level for Jan 2021`:`20c. What was your Occupancy level for Mar 2021`, Business_name = `1. What is the Company/Organisation/Business name?`) %>% left_join(covdata %>% select(`20a. What was your Occupancy level for Jan 2021`:`20c. What was your Occupancy level for Mar 2021`, Business_name = `1. What is the Company/Organisation/Business name?`) %>% mutate(Average =round(rowMeans(select(., `20a. What was your Occupancy level for Jan 2021`:`20c. What was your Occupancy level for Mar 2021`), na.rm = T)))) %>% select(Business_name, everything()) %>% kable()
```

Table 19: Room Cancellations and losses										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(Business_name = `1. What is the Company/Organisation/Business name?`, `24a. How many room cancellations have you had in the last one year`, `24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)%>% filter(!is.na(`24a. How many room cancellations have you had in the last one year`) & !is.na(`24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)) %>% bind_rows(
covdata %>% select(Business_name = `1. What is the Company/Organisation/Business name?`, `24a. How many room cancellations have you had in the last one year`, `24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`) %>% melt(id = 'Business_name') %>% group_by(variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% mutate(Business_name = 'Average')) %>% mutate_if(is.numeric, round)  %>%  kable()
```

Table 19: Room Cancellations and losses	by business type:
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata %>% select(Business_type = `2. Type of Business`, `24a. How many room cancellations have you had in the last one year`, `24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)%>% filter(!is.na(`24a. How many room cancellations have you had in the last one year`) & !is.na(`24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)) %>% melt(id = 'Business_type') %>% group_by(Business_type, variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% bind_rows(
covdata %>% select(Business_type = `2. Type of Business`, `24a. How many room cancellations have you had in the last one year`, `24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)%>% filter(!is.na(`24a. How many room cancellations have you had in the last one year`) & !is.na(`24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)) %>% melt(id = 'Business_type') %>% group_by(variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% mutate(Business_type = 'Average'))%>% mutate_if(is.numeric, round)%>%  kable()
```

Table 19: Room Cancellations and losses	by business age:
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata%>% mutate(`7. How do you rate your business performance in the last 12 months?` = factor(`7. How do you rate your business performance in the last 12 months?`, levels = c('Poor', 'Fair', 'Good')), `4. Years in Business of the Company` = factor(`4. Years in Business of the Company`, levels = c('0-3years', '4-6 years', '7-9 years', '10-12 years', '13-15 years', '15+ years'))) %>% select(Business_years = `4. Years in Business of the Company`, `24a. How many room cancellations have you had in the last one year`, `24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)%>% filter(!is.na(`24a. How many room cancellations have you had in the last one year`) & !is.na(`24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)) %>% melt(id = 'Business_years') %>% group_by(Business_years, variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% bind_rows(
covdata %>% select(Business_years = `4. Years in Business of the Company`, `24a. How many room cancellations have you had in the last one year`, `24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)%>% filter(!is.na(`24a. How many room cancellations have you had in the last one year`) & !is.na(`24b. How much have you lost in revenues due to room cancellations in Uganda Shillings in the last one year`)) %>% melt(id = 'Business_years') %>% group_by(variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% mutate(Business_years = 'Average'))%>% mutate_if(is.numeric, round)%>%  kable()
```

Booking Patterns										
Table 20: Number of Bookings by tourist type										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`2. Type of Business`, `10a1. How many bookings of Foreign tourists did you make during the Periods Jul-Aug 2020;`:`10d4. How many bookings did you make during the Periods Jan-Mar 2021=${bookings_janmar}`) %>%melt(id = "2. Type of Business") %>% mutate(Period = case_when(str_detect(variable, "Jul-Aug 2020")~"Jul-Aug 2020",str_detect(variable, "Sep-Oct 2020")~"Sep-Oct 2020", str_detect(variable, "Nov-Dec 2020")~"Nov-Dec 2020", str_detect(variable, "Jan-Mar 2021")~"Jan-Mar 2021",), Tourist = case_when(str_detect(variable, 'Foreign')~'Foreign tourists', str_detect(variable, 'Domestic')~'Domestic tourists', )) %>% mutate(value = as.numeric(value),Period = factor(Period, levels = c( "Jul-Aug 2020","Sep-Oct 2020",  "Nov-Dec 2020", "Jan-Mar 2021" )) ) %>% group_by(Tourist, Period) %>% summarise(N=  sum(value, na.rm = T)) %>% drop_na(Tourist) %>% pivot_wider(names_from = 'Period', values_from = 'N')
```

Table 21: Number of Bookings by Business Type:
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select( `2. Type of Business`, `10a1. How many bookings of Foreign tourists did you make during the Periods Jul-Aug 2020;`:`10d4. How many bookings did you make during the Periods Jan-Mar 2021=${bookings_janmar}`) %>%melt(id = "2. Type of Business") %>% mutate(Period = case_when(str_detect(variable, "Jul-Aug 2020")~"Jul-Aug 2020",str_detect(variable, "Sep-Oct 2020")~"Sep-Oct 2020", str_detect(variable, "Nov-Dec 2020")~"Nov-Dec 2020", str_detect(variable, "Jan-Mar 2021")~"Jan-Mar 2021",), Tourist = case_when(str_detect(variable, 'Foreign')~'Foreign tourists', str_detect(variable, 'Domestic')~'Domestic tourists', )) %>% mutate(value = as.numeric(value),Period = factor(Period, levels = c( "Jul-Aug 2020","Sep-Oct 2020",  "Nov-Dec 2020", "Jan-Mar 2021" )) ) %>% drop_na(value) %>% group_by( `2. Type of Business`, Period) %>% summarise(N=  sum(value, na.rm = T)) %>% drop_na( `2. Type of Business`) %>% pivot_wider(names_from = 'Period', values_from = 'N')
```

Table 22: Number of Foreign Bookings by Business Type										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select( `2. Type of Business`, `10a1. How many bookings of Foreign tourists did you make during the Periods Jul-Aug 2020;`:`10d4. How many bookings did you make during the Periods Jan-Mar 2021=${bookings_janmar}`) %>%melt(id = "2. Type of Business") %>% mutate(Period = case_when(str_detect(variable, "Jul-Aug 2020")~"Jul-Aug 2020",str_detect(variable, "Sep-Oct 2020")~"Sep-Oct 2020", str_detect(variable, "Nov-Dec 2020")~"Nov-Dec 2020", str_detect(variable, "Jan-Mar 2021")~"Jan-Mar 2021",), Tourist = case_when(str_detect(variable, 'Foreign')~'Foreign tourists', str_detect(variable, 'Domestic')~'Domestic tourists', )) %>% mutate(value = as.numeric(value),Period = factor(Period, levels = c( "Jul-Aug 2020","Sep-Oct 2020",  "Nov-Dec 2020", "Jan-Mar 2021" ))) %>% drop_na(value)%>% filter(Tourist == "Foreign tourists") %>% group_by( `2. Type of Business`, Period) %>% summarise(N=  sum(value, na.rm = T)) %>% drop_na( `2. Type of Business`) %>% pivot_wider(names_from = 'Period', values_from = 'N')
```

Table 23: Number of Domestic Bookings by Business Type
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select( `2. Type of Business`, `10a1. How many bookings of Foreign tourists did you make during the Periods Jul-Aug 2020;`:`10d4. How many bookings did you make during the Periods Jan-Mar 2021=${bookings_janmar}`) %>%melt(id = "2. Type of Business") %>% mutate(Period = case_when(str_detect(variable, "Jul-Aug 2020")~"Jul-Aug 2020",str_detect(variable, "Sep-Oct 2020")~"Sep-Oct 2020", str_detect(variable, "Nov-Dec 2020")~"Nov-Dec 2020", str_detect(variable, "Jan-Mar 2021")~"Jan-Mar 2021",), Tourist = case_when(str_detect(variable, 'Foreign')~'Foreign tourists', str_detect(variable, 'Domestic')~'Domestic tourists', )) %>% mutate(value = as.numeric(value),Period = factor(Period, levels = c( "Jul-Aug 2020","Sep-Oct 2020",  "Nov-Dec 2020", "Jan-Mar 2021" ))) %>% drop_na(value) %>% filter(Tourist == "Domestic tourists") %>% group_by( `2. Type of Business`, Period) %>% summarise(N=  sum(value, na.rm = T)) %>% drop_na( `2. Type of Business`) %>% pivot_wider(names_from = 'Period', values_from = 'N')
```

Table 24: Average Bookings by Business type										
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select( `2. Type of Business`, `10a1. How many bookings of Foreign tourists did you make during the Periods Jul-Aug 2020;`:`10d4. How many bookings did you make during the Periods Jan-Mar 2021=${bookings_janmar}`) %>%melt(id = "2. Type of Business") %>% mutate(Period = case_when(str_detect(variable, "Jul-Aug 2020")~"Jul-Aug 2020",str_detect(variable, "Sep-Oct 2020")~"Sep-Oct 2020", str_detect(variable, "Nov-Dec 2020")~"Nov-Dec 2020", str_detect(variable, "Jan-Mar 2021")~"Jan-Mar 2021",), Tourist = case_when(str_detect(variable, 'Foreign')~'Foreign tourists', str_detect(variable, 'Domestic')~'Domestic tourists', )) %>% mutate(value = as.numeric(value),Period = factor(Period, levels = c( "Jul-Aug 2020","Sep-Oct 2020",  "Nov-Dec 2020", "Jan-Mar 2021" ))) %>% drop_na(value) %>% group_by( `2. Type of Business`, Period) %>% summarise(N= round(mean(value, na.rm = T))) %>% drop_na( `2. Type of Business`) %>% pivot_wider(names_from = 'Period', values_from = 'N')
```

Table 25: Experiencing Cancellations of Bookings:
**This section had NAs that i filtered out. Thats why the total is less than the number of surveys conducted**
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% drop_na(`11. Have you had any cancellations of bookings in the last 12 months?`) %>% group_by(`11. Have you had any cancellations of bookings in the last 12 months?`)  %>% summarise(Count = n()) %>% mutate(Per = paste0(round(Count/sum(Count)*100), '%')) %>% adorn_totals(where = 'row')  %>% kable()
```

Table 26: Number and average cancellations and Loss in revenues by business type										
Averages:
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata %>% select(Business_type = `2. Type of Business`, `12. How many bookings have been cancelled in the last 12 months?`, `13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)%>% filter(!is.na(`12. How many bookings have been cancelled in the last 12 months?`) & !is.na(`13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)) %>% melt(id = 'Business_type') %>% group_by(Business_type, variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% bind_rows(covdata %>% select(Business_type = `2. Type of Business`, `12. How many bookings have been cancelled in the last 12 months?`, `13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)%>% filter(!is.na(`12. How many bookings have been cancelled in the last 12 months?`) & !is.na(`13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)) %>% melt(id = 'Business_type') %>% group_by(variable) %>% summarise(value = mean(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% mutate(Business_type = 'Average'))%>% mutate_if(is.numeric, round)%>%  kable()
```

Totals/Summations
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata %>% select(Business_type = `2. Type of Business`, `12. How many bookings have been cancelled in the last 12 months?`, `13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)%>% filter(!is.na(`12. How many bookings have been cancelled in the last 12 months?`) & !is.na(`13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)) %>% melt(id = 'Business_type') %>% group_by(Business_type, variable) %>% summarise(value = sum(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% bind_rows(covdata %>% select(Business_type = `2. Type of Business`, `12. How many bookings have been cancelled in the last 12 months?`, `13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)%>% filter(!is.na(`12. How many bookings have been cancelled in the last 12 months?`) & !is.na(`13. How much is the estimated loss due to cancellations in terms of revenues in the last 12 months? Please provide response UGShs`)) %>% melt(id = 'Business_type') %>% group_by(variable) %>% summarise(value = sum(value, na.rm = T)) %>% pivot_wider(names_from = 'variable', values_from ='value' ) %>% mutate(Business_type = 'Average'))%>% mutate_if(is.numeric, round)%>%  kable()
```

Table 27: Reasons for Cancellation of Bookings	
```{r, echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata %>% select(`14. What are some of the reasons for cancellation of bookings? (tick the relevant boxes)/Hesitancy to travel`:`14. What are some of the reasons for cancellation of bookings? (tick the relevant boxes)/Others (Specify)`) %>% melt() %>% mutate(Reason = case_when(str_detect(variable, "Hesitancy to travel")~"Hesitancy to travel", str_detect(variable, "Travel restrictions")~"Travel restrictions", str_detect(variable, "Lockdown")~"Lockdown that being imposed", str_detect(variable, "money")~"No money for travel",)) %>% drop_na(Reason) %>% group_by(Reason) %>% summarise(Count = sum(value, na.rm = T)) %>% mutate(per = paste0(round(Count/sum(Count)*100), '%'))%>%  kable()


```

Other reasons:

```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
library(tidytext)
library(wordcloud)
library(RColorBrewer)

effect<-  covdata %>% select(value = `14a. Other (Specify)`) 
effect %>% select(value) %>% mutate(bigram = str_to_lower(value))  %>%unnest_tokens(word, value, token = 'ngrams', n = 1) %>% filter(!word %in% stop_words$word) %>% count(word, sort = T) %>% drop_na(word) -> nn

pal <- brewer.pal(8,"Dark2")
wordcloud(nn$word, nn$n, scale=c(8,.2),min.freq=2, max.words=Inf, random.order=FALSE, rot.per=.15, colors=pal)
```

MICE-Meetings, Incentives, Conferences and Events										
Table 28: Volumes of Conferences held in the last one year. There are some outlier in this data set. These need to be question.
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
options(scipen=999)
covdata %>% select(Company = `1. What is the Company/Organisation/Business name?`, Conferences_held =  `22. How many conferences did you hold in the last one year`,Average_attendance = `23. How many participants on average attended each of the conferences in the last one year`) %>% mutate(Estimate = Conferences_held * Average_attendance, Average_attendance = as.numeric(Average_attendance)) %>% filter( !(is.na(Conferences_held) & is.na(Average_attendance)) ) %>% arrange(Company)%>%  kable()
```

Outliers: The data need to be cleaned for these since they appear to be out of the norm.

```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
options(scipen=999)
covdata %>% select(Company = `1. What is the Company/Organisation/Business name?`, Conferences_held =  `22. How many conferences did you hold in the last one year`,Average_attendance = `23. How many participants on average attended each of the conferences in the last one year`) %>% mutate(Estimate = Conferences_held * Average_attendance, Average_attendance = as.numeric(Average_attendance)) %>% filter( !(is.na(Conferences_held) & is.na(Average_attendance)) ) %>% arrange(desc(Average_attendance)) %>% top_n(n = 8)%>%  kable()
```

Using averages: (I have removed the outliers above)
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata %>% select(Conferences_held =  `22. How many conferences did you hold in the last one year`,Average_attendance = `23. How many participants on average attended each of the conferences in the last one year`) %>% filter(Average_attendance<4000000) %>% melt() %>% group_by(variable) %>% summarise(Average = mean(value, na.rm = T)) %>%  kable()

```

Table 29: Hosting of Conferences:
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% group_by(Response = `21. Did you host any conferences in the last one year`) %>% drop_na(`21. Did you host any conferences in the last one year`) %>% summarise(count = n()) %>% mutate(`Percent (%)` =paste0(round(count/sum(count)*100), "%")) %>% adorn_totals(where = 'row')%>%  kable()

```

Incomes in 2020						
Table 30: Receipt of change in income.
The average is influenced by outliers. I have therefore dropped any record below 10000. This only drops one record.
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`, `16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`)  %>% drop_na(`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`) %>% filter(`16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`>1000) %>% group_by(Response=`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`) %>% summarise(Count = n(), Average_change = mean(`16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`)) %>% mutate(`percent(%)`=paste0(round(Count/sum(Count)*100),"%")) %>% kable()
```

By business type {#test}
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`2. Type of Business`, `15. Have you had a decline or increase in your sales in the last 12 months compared to before?`, `16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`)  %>% drop_na(`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`) %>% filter(`16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`>1000) %>% group_by(`2. Type of Business`, Response=`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`) %>% summarise(Count = n(), Average_change = mean(`16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`)) %>% ungroup() %>%  mutate(`percent(%)`=paste0(round(Count/sum(Count)*100),"%")) %>% kable()
```

Outlier record from the previous table:
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`1. What is the Company/Organisation/Business name?`, `2. Type of Business`, `15. Have you had a decline or increase in your sales in the last 12 months compared to before?`, `16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`)  %>% drop_na(`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`) %>% filter(`16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`<1000)%>% kable()
```

Table 31: Lost income in the last one year
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`27. What is the level of income lost over the last one year/Less than 25% of income lost`:`27. What is the level of income lost over the last one year/No income lost`) %>% melt() %>% mutate(Response = case_when(str_detect(variable, "Less than 25% of income lost") ~"Less than 25% of income lost", str_detect(variable, "Less than 50% of income lost")~"Less than 50% of income lost", str_detect(variable, "Over 50% of income lost")~"Over 50% of income lost", str_detect(variable, "100% of income lost")~ '100% of income lost', str_detect(variable, "No income lost")~"No income lost",)) %>% mutate(Response, factor(Response, levels = c('No income lost', "Less than 25% of income lost", "Less than 50% of income lost", "Over 50% of income lost","100% of income lost")))  %>% group_by(Response) %>% summarise(Count = sum(value, na.rm = T)) %>% mutate(per = paste0(round(Count/sum(Count)*100), '%')) %>% arrange(Response) %>%  kable()
```

Business prospects for 2021 and Stimulus Package required						
Table 32: View of the Business Prospects for 2021
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(Business_prospects=`28. How do you see the business prospects for the year 2021`) %>% drop_na(Business_prospects) %>% mutate(Business_prospects = factor(Business_prospects, levels = c('Worse', 'Bad', 'Fair', 'Good', 'Very Good'))) %>% group_by(Business_prospects) %>% summarise(count=n())%>% mutate(`percent(%)`= paste0(round(count/sum(count)*100),"%")) %>% adorn_totals(where = 'row') %>% kable()
```

Table 33: View of the Business Prospects for 2021 by Business Type
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(Business_prospects=`28. How do you see the business prospects for the year 2021`,`Type of Business` = `2. Type of Business`) %>% drop_na(Business_prospects) %>% mutate(Business_prospects = factor(Business_prospects, levels = c('Worse', 'Bad', 'Fair', 'Good', 'Very Good'))) %>% group_by(Business_prospects, `Type of Business`) %>% summarise(count=n()) %>% pivot_wider(values_from = count, names_from = Business_prospects)  %>% adorn_totals(where =c('row', 'col')) %>% mutate_if(is.numeric, replace_na, "") %>% kable()
```

Table 34: View of the Business Prospects for 2021 by Business Type
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`29. What Stimulus package would you wish government to provide to the Tourism industry to help in recovery and boost tourism?/Provide Loan Grace Period to Tourism Business`:`29. What Stimulus package would you wish government to provide to the Tourism industry to help in recovery and boost tourism?/Others (Specify)`) %>% melt() %>% mutate(Stimulus_package = case_when(
str_detect(variable, "Provide Loan Grace period to Tourism Business")~"Provide Loan Grace period to Tourism Business", str_detect(variable, "Provide lower interest rates")~"Provide lower interest rates", 
str_detect(variable, "Tax reductions or deferments")~"Tax reductions or deferments", 
str_detect(variable, "Intensify marketing and promotion of Domestic Tourism to support Tourism business")~"Intensify marketing and promotion of Domestic Tourism to support Tourism business",
str_detect(variable, "Financial support for cash flow and recovery")~"Financial support for cash flow and recovery",
str_detect(variable, "Expert advice on business strategy and recovery")~"Expert advice on business strategy and recovery",
str_detect(variable, "Virtual training for upskilling entrepreneurs and staff")~"Virtual training for upskilling entrepreneurs and staff",
str_detect(variable, "Commercial debt repayment support")~"Commercial debt repayment support",
str_detect(variable, "Others (Specify)")~"Others",)) %>% drop_na(Stimulus_package) %>% group_by(Stimulus_package) %>% summarise(Count = sum(value, na.rm = T)) %>% mutate(per = paste0(round(Count/sum(Count)*100), '%'))%>%  kable()
```

Airlines and Flights						
Table 35: Number of Flights per year: This question was captured wrongly. It was captured as a boolean data type and not numeric. Hence the table summarises yes/no responses.
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}

covdata %>% select(`2. Type of Business`, `8a. State the number of flights made per week in 2019 for your Airline?`:`8c. State the number of flights made per week in 2021 for your Airline?`) %>% melt(id = '2. Type of Business') %>% select(-`2. Type of Business`) %>% mutate(Flight = case_when(str_detect(variable, "2019 for your Airline")~"Number of flights per week in 2019",str_detect(variable, "2020 for your Airline")~"Number of flights per week in 2020", str_detect(variable, "2021 for your Airline")~"Number of flights per week in 2021" ), ) %>% drop_na(Flight) %>% group_by(Flight) %>% summarise(Count = sum(value, na.rm = T)) %>% mutate(per = paste0(round(Count/sum(Count)*100), '%'))%>%  kable()
```

Table 36: Number of Flights per year by Airline:
This question was not for each flight company.


Table 37: Have you grounded any of your fleet of Aero planes.
This question was also not captured by the questionnaire.

```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% drop_na(`9. Have you grounded any of your fleet of Aero planes? (for Airlines only)`) %>% group_by(`9. Have you grounded any of your fleet of Aero planes? (for Airlines only)`) %>% summarise(N = n())
```

Sales of Souvenirs and Handicrafts						
Table 38: Souvenir and Handicraft Sales
Similar to tables in [group tables 30](#test)

Table 39: Souvenir and Handicraft Sales
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% select(`1. What is the Company/Organisation/Business name?`, `15. Have you had a decline or increase in your sales in the last 12 months compared to before?`, `16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`)  %>% drop_na(`15. Have you had a decline or increase in your sales in the last 12 months compared to before?`) %>% filter(`16. If your answer is increase or declines, How much is the estimated loss/increase you have got for the last one year in Uganda Shillings due to COVID-19`>1000) %>% group_by(`1. What is the Company/Organisation/Business name?`)  %>% kable()
```

Domestic Tourism					
Table 40: Can Tourism in Uganda survive without International Tourists inflows						
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% group_by(Response = `30a. Can Tourism survive without International Tourists inflows?`) %>% drop_na(`30a. Can Tourism survive without International Tourists inflows?`) %>% summarise(count=n()) %>% mutate(`percent(%)`=paste0(round(count/sum(count)*100),"%")) %>% adorn_totals(where = 'row') %>% kable()
```

Table 41: Suggestions to develop the domestic tourism industry:

```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
effect<-  covdata %>% select(value = `30b. Provide suggestions on how government encourage domestic tourists to travel?`) 
effect %>% select(value) %>% mutate(bigram = str_to_lower(value))  %>%unnest_tokens(word, value, token = 'ngrams', n = 1) %>% filter(!word %in% stop_words$word) %>% count(word, sort = T) %>% drop_na(word) -> nn

pal <- brewer.pal(8,"Dark2")
wordcloud(nn$word, nn$n, scale=c(8,.2),min.freq=2, max.words=Inf, random.order=FALSE, rot.per=.15, colors=pal)
```

Table 42: Do you think there has been growth in Domestic Tourism over the last one year
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
covdata %>% group_by(Response = `30c. Do you think there has been growth in Domestic Tourism over the last one year?`) %>% drop_na(`30c. Do you think there has been growth in Domestic Tourism over the last one year?`) %>% summarise(count=n()) %>% mutate(`percent(%)`=paste0(round(count/sum(count)*100),"%")) %>% adorn_totals(where = 'row') %>% kable()
```

Table 43: Barriers to growth in Domestic Tourism in 2020

```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
effect<-  covdata %>% select(value = `30d. What do you think has limited growth in Domestic Tourism over the last one year?`) 
effect %>% select(value) %>% mutate(bigram = str_to_lower(value))  %>%unnest_tokens(word, value, token = 'ngrams', n = 1) %>% filter(!word %in% stop_words$word) %>% count(word, sort = T) %>% drop_na(word) -> nn

pal <- brewer.pal(8,"Dark2")
wordcloud(nn$word, nn$n, scale=c(8,.2),min.freq=2, max.words=Inf, random.order=FALSE, rot.per=.15, colors=pal)
```


Table 44: Factors that have led to growth of Domestic Tourism in 2020:
```{r , echo=FALSE, message=FALSE, warning=FALSE,error=FALSE, comment=NA}
effect<-  covdata %>% select(value = `30e. What do you think has led to growth of Domestic Tourism over the last one year?`) 
effect %>% select(value) %>% mutate(bigram = str_to_lower(value))  %>%unnest_tokens(word, value, token = 'ngrams', n = 1) %>% filter(!word %in% stop_words$word) %>% count(word, sort = T) %>% drop_na(word) -> nn

pal <- brewer.pal(8,"Dark2")
wordcloud(nn$word, nn$n, scale=c(8,.2),min.freq=2, max.words=Inf, random.order=FALSE, rot.per=.15, colors=pal)
```

 <a href="#top">Back to top</a>